SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-04 back.tex
detail about perc learning rule

>>>>

%ETG: this is what I had added about perceptrons, we're trying to 
%figure out what to leave and what to get rid of ...  
\subsection{Perceptron-based Prediction}

Perceptrons in microarchitecture were first introduced by Jimenez and Lin ~\cite{Perc_Branch} for branch prediction. In this work, a perceptron weights vector is selected by a hash of the branch address and its dot product with an input vector of branch history outcomes. If the product is at least 0, the branch is predicted as taken, otherwise it is predicted not taken. The weights are updated with the perceptron update rule: if the prediction is incorrect, or the dot product does not exceed some threshold magnitude, then the weights are incremented or decremented based on their correlation to the corresponding history bits. Perceptron learning yields to superior accuracy, which results in increased opportunity for optimizations.

\subsubsection{Perceptron Learning}

In a perceptron-based mechanism, a uniform
perceptron update principle is followed.  Perceptrons are a simple model of neurons
in neural networks \cite{perceptrons1,perceptrons2} modeled by vectors of signed weights learned through online training. The output of a perceptron is the dot product of the weights and a vector of inputs. In this work, we make use of the perceptron learning algorithm. There are two components to the abstract perceptron learning algorithm:

\begin{enumerate}
\item To predict true or false, a vector of signed weights is chosen according to some criteria. The dot product of the weights and input vectors, called $y_{\mbox{\small out}}$, is computed. If $y_{\mbox{\small out}}$ exceeds some threshold, the prediction is true, otherwise it is false.

\item To update the weights after the true outcome of the predicted event is
known, we first consider the value of $y_{\mbox{\small out}}$. If the
prediction was correct and $|y_{\mbox{\small out}}|$ exceeds a threshold
$\theta$, then the weights remain unchanged. Otherwise, the inputs are used to
update the corresponding weights.  If there is positive correlation between
the input and the outcome of the event, the corresponding weight is
incremented; otherwise, it is decremented. Over time, the weights are
proportional to the probability that the outcome of the event is true in the
context of the input and the criterion for choosing that weight. The weights
saturate at maximum and minimum values so they will fit in a fixed bit width.
\end{enumerate}
